A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-07 evaluation.tex
Update results

The benchmarks are executed in parallel across a cluster of identical
machines, \BenchmarkRig{}, as the sole job for each machine.  We compiled
the code using Scala~\ScalaVersion{} and executed the experiments
on~\JvmVersion{} with a maximum heap of~\MaxHeapSize{}. We used \Nuxmv{}
version~\NuxmvVersion{} invoked as a subprocess for each instance. Instances
were executed in batches of \BatchSize{}, each given a fresh JVM. Each JVM was
warmed up for \SI{10}{s} on a random benchmark from the set before starting
to execute. We believe this represents a realistic use case where \Calculus{} is
used to support, e.g., a string solver. Experiments were executed in random order
for all backends. Each instance got a time budget of~\RuntimeTimeout{}.

@@

\subsubsection{Scalability}\label{sec:scaling}%
To investigate scaling we additionally execute \numprint{2000} randomly sampled
(without replacement) benchmarks with a \numprint{120}-second timeout. We add
runs of \Calculus{} with clause learning and restarts disabled, and with only
clause learning disabled to show the impact of \cref{sec:random-restarts}, and
\cref{sec:clause-learning} respectively.

@@

The most obvious threat to validity would be an unsound implementation. To
address this we have validated all reported solutions made by \Calculus{} with
\Nuxmv{}. A previous version contained a race with random restarts during
product materialisation causing non-deterministic unsoundness in \numprint{0.7}
of instances. Additionally, both we and the artefact evaluation committee independently
discovered a soundness issue in CA-Str on one instance in QF\_S where the 
\texttt{QF\_S\slash{}20230329-automatark-lu\slash{}instance08425.smt2} instance was
incorrectly reported as \textsc{Unsat}. The underlying issue was that \Catra{} generated
a too broad blocking clause when encountering unsatisifiability stemming from 
an intermittent product accepting only the empty string during product materialisation. 
We implemented a fix for that bug and re-evaluated all benchmarks in SMT-COMP.

Since addressing those bugs we have observed no further soundness
issues in neither \Catra{} nor CA-Str. Benchmarking results for both runs are included
in the artefact of this paper, and show virtually identical performance characteristics.

>>>>

The benchmarks for \Calculus{} and \Nuxmv{} are executed in parallel on \BenchmarkRig{}, with 4~threads
sharing the same JVM.  The baseline implementation was executed as one single job per
instance on StarExec, with the same configuration as CA-Str and \Ostrich{} used in SMT-COMP since
it could not be executed reliably in less than a week on our machine.

We compiled
the code using Scala~\ScalaVersion{} and executed the experiments
on~\JvmVersion{} with a maximum heap of~\MaxHeapSize{}. We used \Nuxmv{}
version~\NuxmvVersion{} invoked as a subprocess for each instance. Instances
were executed in batches of \BatchSize{}, each given a fresh JVM. Each JVM was
warmed up for \SI{10}{s} on a random benchmark from the set before starting
to execute. We believe this represents a realistic use case where \Calculus{} is
used to support, e.g., a string solver. Experiments were executed in random order
for all backends. Each instance got a time budget of~\RuntimeTimeout{}.

@@

\subsubsection{Scalability}\label{sec:scaling}%
To investigate scaling we additionally execute \numprint{2000} randomly sampled
(without replacement) benchmarks with a \numprint{120}-second timeout. We add
runs of \Calculus{} with clause learning and restarts disabled, and with only
clause learning disabled to show the impact of \cref{sec:random-restarts}, and
\cref{sec:clause-learning} respectively. These experiments are executed on a smaller
machine, a six-core AMD~Ryzen~5 2600 but the same Java version. Their max
heap size is set to \SI{20}{GB} since this system has less RAM. The baseline
experiments are executed separately as only two threads, since the implementation is
so RAM-hungry it is difficult to benchmark reliably under longer timeouts.

@@

The most obvious threat to validity would be an unsound implementation. To
address this we have validated all reported solutions made by \Calculus{} with
\Nuxmv{}. A previous version contained a race with random restarts during
product materialisation causing non-deterministic unsoundness in \numprint{0.7}
of instances. Additionally, both we and the artefact evaluation committee independently
discovered a soundness issue in CA-Str on one instance in QF\_S where the 
\texttt{QF\_S\slash{}20230329-automatark-lu\slash{}instance08425.smt2} instance was
incorrectly reported as \textsc{Unsat}. The underlying issue was that \Catra{} generated
a too broad blocking clause when encountering unsatisifiability stemming from 
an intermittent product accepting only the empty string during product materialisation. 
We implemented a fix for that bug and re-evaluated all benchmarks.

Since addressing those bugs we have observed no further soundness
issues in neither \Catra{} nor in CA-Str. Benchmarking results for both runs are included
in the artefact of this paper, and show virtually identical performance characteristics,
with the exception for higher efficiency due to better benchmarking machines. We have
additionally performed several of the benchmarks (in particular the \SI{120}{s} experiments)
on machines and clusters of machines with widely different performance characteristics
and have observed the trends to be surprisingly robust.
